### 2014-10-21 Publications/2013-TMI/03-introduction.tex
updated all

\IEEEPARstart{F}{usion} of information from different images is a difficult
  task in image processing, especially when the scale of the imaged structures
  is in the range of the image resolution or below.
In the case of the human brain, the cortex has a typical thickness of up to 5 mm
  \citep{fischl_measuring_2000}.
Moreover, as the cortex is densely folded, points located afar in the topological
  manifold of the brain's surface can be very close in the corresponding 3D space.
Consequently, accuracy and precision are very difficult to achieve, but necessary properties
  of registration algorithms.

In this paper we propose a novel registration framework to simultaneously
solving the segmentation, distortion and cortical parcellation challenges,
by exploiting as strong shape-prior the detailed morphology extracted
from high-resolution and anatomically correct \gls{mri}.
Indeed, hereafter
we assume this segmentation problem in anatomical images is reliably and
accurately solved with readily available tools (e.g.
\citep{fischl_freesurfer_2012}).
After global alignment with \gls{t1} using existing approaches, the remaining
spatial mismatch between anatomical and diffusion space is due to susceptibility
distortions.
Finally, we need to establish precise spatial correspondence between the
surfaces in both spaces, including the tangential direction for parcellation.
Therefore, we can reduce the problem to finding the differences of spatial
distortion in between anatomical and \gls{dwi} space.
We thus reformulate the segmentation problem as an inverse problem, where we
seek for an underlying deformation field (the distortion) mapping
from the structural space into the diffusion space, such that the structural
contours segment optimally the \gls{dwi} data.
In the process, the one-to-one
correspondence between the contours in both spaces is guaranteed, and projection
of parcellisation to \gls{dwi} space is implicit and consistent.

We test our proposed joint segmentation-registration model on two different
synthetic examples.
The first example is a scalar sulcus model, where the
\gls{csf}-\gls{gm} boundary particularly suffers from \gls{pve} and can only be
segmented correctly thanks to the shape prior and its coupling with the inner,
\gls{gm}-\gls{wm} boundary through the imposed deformation field regularity.
The second case deals with more realistic \gls{dwi} data stemming from
phantom simulations of a simplistic brain data.
Again, we show that the
proposed model successfully segments the \gls{dwi} data based on two derived
scalar features, namely \gls{fa} and \gls{md}, while establishing an estimate
of the dense distortion field.

The rest of this paper is organized as follows.
First, in \autoref{sec:methods}
we introduce our proposed model for joint multivariate segmentation-registration.
Then we provide a more detailed description of the data and experimental setup in
\autoref{sec:experiments}.
We present results in \autoref{sec:results} and conclude
in \autoref{sec:conclusion}.

>>>>

\IEEEPARstart{N}{onlinear} registration of images is a challenging task ubiquitous
  in an endless number of image analysis applications.
The problem is solved finding a spatial mapping $U$ that aligns the
  information given in two different coordinate systems (generally called
  \emph{reference}, $R$, and \emph{moving}, $M$):
  \begin{align}
  U\colon R \subset \mathbb{R}^n &\to M \subset \mathbb{R}^n \notag\\
  \vec{r} &\mapsto \vec{r}' =\vec{r}+u(\vec{r}),
  \label{eq:transform}
  \end{align}
  where $\vec{r}$ denotes a position in the reference domain and $\vec{r}'$
  its corresponding location in the target, and $n$ the dimension of domains
  ($n=3$ for 3D images).
Finally, $\vec{u} = u(\vec{r})$ is the function that models the displacement
  of every point in the reference domain.

The wide range of applications has derived in an intensive generation of diverse
  registration methods.
In a recent and comprehensive survey by \citeauthor{sotiras_deformable_2013}
  \citep{sotiras_deformable_2013}, registration methods are classified by
  matching criteria, deformation model, and optimization method.
The most widespread matching criteria are probably the so-called \emph{iconic
  methods} in \citep{sotiras_deformable_2013}.
However they are not appropriate for all the registration problems
  \citep{greve_accurate_2009}.
They propose a \emph{hybrid method} \citep{sotiras_deformable_2013} for the
  intra-subject registration of \gls*{t1} \gls*{mri} and \gls*{dmri} images
  of the brain using a linear transformation model.
As in \citep{greve_accurate_2009}, we exploit the precise structures that
  can be readily extracted with widely-used tools at high resolution
  and map this prior information to low resolution data,
  in which the scale of the imaged structures is in the range of the image
  resolution or above.
Our approach differs with \citep{greve_accurate_2009} in two fundamental
  choices: 1) We use a nonlinear deformation model that enables the
  correction of the susceptibility-derived distortions
  \citep{jezzard_correction_1995} that \gls*{dmri} data typically present.
And 2) our matching criteria does not necessarily need for clear intensity
  steps at the tissue interfaces where surfaces must be fitted.

\subsection{Related work}
\label{sec:methods_background}
Registration-segmentation methods are typically built including a deformation
  model to guide the evolution of a segmentation algorithm.
Even though some Bayesian approaches have been proposed to solve the joint problem
  \citep{wyatt_map_2003}, segmentation is usually performed using an evolving
  active contour \citep{chan_active_2001} that normally includes a shape prior
  term to the energy functional \citep{chen_using_2002,bresson_variational_2006,
  chan_level_2005,cremers_kernel_2006,gastaud_combining_2004}.
These methods generally have an explicit description of the expected relative boundary
  locations of the object to be delineated, and some, even model the statistical deviations
  from this average shape.

An early ``morphing''-segmentation approach was proposed in \citep{bertalmio_morphing_2000},
  and the first proper registration method was presented by \citeauthor{yezzi_variational_2001}
  \citep{yezzi_variational_2001}, where the energy functional is defined simultaneously in the target
  and reference images with an affine transformation supporting the coordinates mapping
  (the so-called ``2 \glspl*{pde} approach'').
\citeauthor{vemuri_joint_2003} proposed the first atlas-based registration \citep{vemuri_joint_2003}
  based on the level-sets framework and using only one \gls*{pde}.
The principal application of these techniques was the image registration between timesteps in
  a time-series or between different images \citep{paragios_level_2003}.
\citeauthor{unal_coupled_2005} \citep{unal_coupled_2005} extended the idea of
  \citep{bertalmio_morphing_2000,yezzi_variational_2001} to nonlinear registration
  using a free deformation field model.
A summary of these second set of techniques is performed in \citep{droske_mumfordshah_2009},
  proposing two different approaches to applying the Mumford-Shah \citep{mumford_optimal_1989}
  functional in joint registration and segmentation, thorugh the propagation of the deformation
  ield from the contours to the whole image definition.
Finally, \citeauthor{gorthi_active_2011} presented a comprehensive generalization of the
  existing methodologies \citep{gorthi_active_2011} based on the level-sets approximation.
Even though the historical evolution of joint segmentation and registration procedures is strongly
  linked to the level sets approximation, our work is based in derivations of the \gls{acwe}
  framework \citep{chan_active_2001}, and related to \citep{guyader_combined_2011}.

Finally, a derivation of the latter group is composed by atlas-based segmentation methods
  \citep{gorthi_segmentation_2009,gorthi_active_2011,pohl_unifying_2005,pohl_bayesian_2006,
  wang_joint_2006}, where the prior imposes consistent voxel-based classification of contiguous
  regions.
A comprehensive summary of the methodologies derived from the \gls{acwe} model, with special attention
  to joint registration-segmentation methods is found in \citep{gorthi_active_2011}.

%{\color{red} {The main diverging points with respect to
%\citep{gorthi_active_2011} are: 1) there is no need for an explicit level set function
%$\Phi_G$, as we replace the level set gradient computation $N_{\Phi_G}$ with shape
%gradients \citep{besson_dream2s_2003,herbulot_segmentation_2006};
%2) regularization is also based on linear diffusion smoothing \citep{thirion_image_1998},
%but we replace the Gaussian filtering by other constraints
%studied in \citep{nagel_investigation_1986} to better the problem;
%3) optimization is applied in the spectral
%domain, observing anisotropic and inhomogeneous mappings along each direction.
%With respect \citep{guyader_combined_2011}, the main differences are
%the distance function, and the spectral solution to the optimization updates,
%as we shall cover in \autoref{sec:numerical_implementation}.}}

\subsection{Susceptibility-derived distortions}

\subsection{Our framework}
\label{sec:our_framework}

%In this paper we formulate the joint registration-segmentation
%problem as follows.
%such that the known contours in anatomical space $T$ optimally segment
%the diffusion space $D$.
%
%
%Whereas related \glspl*{adf} introduced in \autoref{sec:methods_background}
%make use of explicit level-set formulations to solve \eqref{eq:gradient_descent},
%we alternatively use \emph{shape-gradients}
%\cite{besson_dream2s_2003,herbulot_segmentation_2006}.

%
%Let us denote by $\vec{x}$ the voxel and $F(\vec{x}) = [ f_1, f_2, \ldots, f_N]^T$
%  its associated feature vector in the following.
%
%In our application, these surfaces are precise tissue interfaces of interest extracted
%  from a high-resolution, anatomically correct reference volume using
%  the well-established
%
%In this paper we propose a novel registration framework to simultaneously
%solving the segmentation, distortion and cortical parcellation challenges,
%by exploiting as strong shape-prior the detailed morphology extracted
%from high-resolution and anatomically correct \gls{mri}.
%Indeed, hereafter
%we assume this segmentation problem in anatomical images is reliably and
%accurately solved with readily available tools (e.g.
%\citep{fischl_freesurfer_2012}).
%After global alignment with \gls{t1} using existing approaches, the remaining
%spatial mismatch between anatomical and diffusion space is due to susceptibility
%distortions.
%Finally, we need to establish precise spatial correspondence between the
%surfaces in both spaces, including the tangential direction for parcellation.
%Therefore, we can reduce the problem to finding the differences of spatial
%distortion in between anatomical and \gls{dwi} space.
%We thus reformulate the segmentation problem as an inverse problem, where we
%seek for an underlying deformation field (the distortion) mapping
%from the structural space into the diffusion space, such that the structural
%contours segment optimally the \gls{dwi} data.
%In the process, the one-to-one
%correspondence between the contours in both spaces is guaranteed, and projection
%of parcellisation to \gls{dwi} space is implicit and consistent.
%
%We test our proposed joint segmentation-registration model on two different
%synthetic examples.
%The first example is a scalar sulcus model, where the
%\gls{csf}-\gls{gm} boundary particularly suffers from \gls{pve} and can only be
%segmented correctly thanks to the shape prior and its coupling with the inner,
%\gls{gm}-\gls{wm} boundary through the imposed deformation field regularity.
%The second case deals with more realistic \gls{dwi} data stemming from
%phantom simulations of a simplistic brain data.
%Again, we show that the
%proposed model successfully segments the \gls{dwi} data based on two derived
%scalar features, namely \gls{fa} and \gls{md}, while establishing an estimate
%of the dense distortion field.
%
%The rest of this paper is organized as follows.
%First, in \autoref{sec:methods}
%we introduce our proposed model for joint multivariate segmentation-registration.
%Then we provide a more detailed description of the data and experimental setup in
%\autoref{sec:experiments}.
%We present results in \autoref{sec:results} and conclude
%in \autoref{sec:conclusion}.
%
%
%The properties of the reconstructed tensors and derived scalar maps have
%been studied by \cite{ennis_orthogonal_2006}. Based on their
%findings, \gls{fa}~\eqref{eq:fa} and \gls{md}~\eqref{eq:md} are
%considered complementary features, and therefore we selected them for the
%energy model \eqref{eq:complete_energy} in driving the
%registration-segmentation process.
%Whereas \gls{fa} informs mainly about the \emph{shape} of diffusion,
%the \gls{md} is more related to the \emph{magnitude} of the process:
%
%\begin{align}
%\mathrm{FA} &= \sqrt{ \frac{1}{2}}\,\frac{\sqrt{ (\lambda_1 - \lambda_2)^2 + (\lambda_2 - \lambda_3)^2 + (\lambda_3 - \lambda_1)^2}}{\sqrt{ {\lambda_1}^2 + {\lambda_2}^2 + {\lambda_3}^2}} \label{eq:fa} \\
%\mathrm{MD} &= ( \lambda_1 + \lambda_2 + \lambda_3 ) / 3 \label{eq:md}
%\end{align}
%where $\lambda_i$ are the eigenvalues of the diffusion tensor
%associated with the diffusion signal $S(\vec{q})$. There exist
%two main reasons to justify their choice.
%First, they are well-understood and standardized in clinical routine.
%Second, together they contain most of the information that is
%usually extracted from the \gls{dwi}-derived scalar maps
%\cite{ennis_orthogonal_2006}.
%

### 2014-10-21 Publications/2013-TMI/04-methods.tex
updated all

First, we assume independence between pixels, and thus break down the
  global data likelihood into a product of pixel-wise conditional probabilities:
  \begin{equation}
  P(F \mid U,\Omega) = \underset{l}{\prod} \underset{\vec{x}\in \Omega_l}{\prod}
    P\left( \vec{f}' \mid U \right),
  \label{eq:bayes_aposteriori}
  \end{equation}
  where $\vec{f}' = F(\vec{x}')$ is the feature vector at the displaced
  position $\vec{x}'$ (\autoref{eq:transform}) of the multispectral target
  volume.
For convenience, and because it has been shown to be appropriate approximations
  \citep{cuadra_comparison_2005}, we introduce two assumptions for each
  region $\Omega_l$:
  1) the features are i.i.d.; and 2) they can be modeled by multivariate normal
  distributions:
  \begin{equation}
  P\left( \vec{f}' \mid U,\Omega_l \right) = \mathcal{N} \left( \vec{f}' \mid \Theta_l \right),
  \label{eq:likelihood}
  \end{equation}
 	where $\Theta_l = \lbrace \boldsymbol{\mu}_l, \boldsymbol{\Sigma}_{l} \rbrace$ are the
 	descriptors of region $\Omega_l$.
We then insert \autoref{eq:likelihood} into \autoref{eq:bayes_rule} to obtain the full
  formulation of the \emph{data term} of our registration model:
 	\begin{align}
  P( F \mid U, \Omega ) &= \underset{l}{\prod} \underset{\vec{x} \in \Omega_l}{\prod}
  \mathcal{N} ( \vec{f} \mid \boldsymbol{\mu}_l, \boldsymbol{\Sigma}_{l} ) \notag\\
  &= \underset{l}{\prod} \underset{\vec{x} \in \Omega_l}{\prod} \frac{1}{ \sqrt{(2\pi)^{C}\,\left|\boldsymbol{\Sigma}_{l}\right|}}\,{e^{\left(-\frac{1}{2}
  \mdist{f'}{l} \right)}},
  \label{eq:pdf}
  \end{align}
  using $\mdist{f}{l}$ to denote the squared \emph{Mahalanobis distance} of $\vec{f}$ with respect
  to the descriptors of region $l$ as
  $\mdist{f}{l} = (\vec{f} - \boldsymbol{\mu}_l)^T \, {\boldsymbol{\Sigma}_l}^{-1} \, (\vec{f} - \boldsymbol{\mu}_l)$.

We choose a Thikonov regularization prior as follows:
  \begin{equation*}
  P(U) = \underset{\vec{x}}{\prod} p(u(\vec{x})),
  \end{equation*}
  with further:
  \begin{align*}
  p(u(\vec{x})) &= p_0(u(\vec{x})) \, p_1(u(\vec{x})) \notag\\
  p_0(u(\vec{x})) &= \mathcal{N}( u(\vec{x}) \mid 0, A^{-1}) \notag\\
  p_1(u(\vec{x})) &= \mathcal{N}(  \nabla \cdot u(\vec{x}) \mid 0, B^{-1}),
  \end{align*}
  imposing that the distortion and its gradient have zero
  mean and variance governed by $A$ and $B$.
Since the anisotropy is generally aligned with the imaging axes, these will be simplified
  in the following for the sake of clarity:
  \begin{align}
    p_0(u(\vec{x})) &= \underset{\vec{x}}{\sum} \mathcal{N}( u(\vec{x}) \mid 0,
      (\boldsymbol{\alpha}^{\circ\frac12}\,\vec{I}_n)^{-1}), \notag\\
    p_1(u(\vec{x})) &= \underset{\vec{x}}{\sum} \mathcal{N}( \nabla \cdot u(\vec{x}) \mid 0,
      (\boldsymbol{\beta}^{\circ\frac12}\,\vec{I}_n)^{-1}).
  \label{eq:priors}
  \end{align}

Finally, the \gls{map} problem is adapted into a variational one applying the
  following log-transform:
  \begin{align}
  E(F \mid U) &= -\log \underset{l}{\prod}
  \underset{\vec{x} \in \Omega_l}{\prod}
  \mathcal{N} \left( \vec{f}' \mid \Theta_l \right)\,p_0( u(\vec{x}))\,p_1( u(\vec{x})), \notag\\
  &= C + \underset{l}{\sum}
  \underset{\vec{x} \in \Omega_l}{\sum}
  \mdist{f'}{l}, \notag\\
  &+ \underset{\vec{x} \in \Omega}{\sum} \boldsymbol{\alpha} \cdot u(\vec{x})^{\circ2}
  + \underset{\vec{x} \in \Omega}{\sum} \boldsymbol{\beta} \cdot (\nabla \cdot u(\vec{x}))^{\circ2},
  \label{eq:energy}
  \end{align}
  that is the dual expression to the energy functional corresponding
  to a discrete \gls*{acwe} framework \citep{chan_active_2001}
  with anisotropic regularization as studied in
  \citep{nagel_investigation_1986}.
We provide a proof of duality in {\color{red} [REF figshare?]}.

@@

\subsubsection{Deformation model}
\label{sec:deformation_model}
Let us denote $\{\vec{c}_i\}_{i=1 \ldots N_c}$ the nodes of one or several prior
  surface(s).
In our application, these surfaces are extracted using \emph{FreeSurfer}
  \citep{fischl_freesurfer_2012} in the case of real datasets.
The transformation from the structural space into the coordinate space of the
  target image is achieved through a dense deformation field $u(\vec{x})$, such that:
  \begin{equation}
  \vec{c}_i' = U\{\vec{c}_i\} = \vec{c}_i + u(\vec{c}_i),
  \label{eq:nodes_tfm}
  \end{equation}
  where $U$ is defined in \eqref{eq:transform}.
Since the nodes of the anatomical surfaces likely lay off-grid, it is required to
  derive $u(\vec{x})$ from a discrete set of parameters $\{\vec{u}_k\}_{k=1 \ldots K}$.
Densification is achieved through a set of associated basis functions $\psi_k$:
  \begin{equation}
  u(\vec{x}) = \sum_k \psi_k(\vec{x}) \vec{u}_k.
  \label{eq:intp_kernel}
  \end{equation}
%
In our implementation, $\psi_k$ is chosen to be a tensor-product B-Spline kernel
  of degree 3 ($B_3$).
Then, introducing \eqref{eq:intp_kernel} into \eqref{eq:nodes_tfm} and replacing
  $\psi$ by the actual kernel function, the transformation writes:
  \begin{equation}
    \vec{c}_i' = \vec{c}_i + \sum_k \left[ \vec{u}_k \, \underset{d}{\prod}
      B_3( (\vec{c}_i - \vec{x}_k) \cdot \hat{\mathbf{e}}_d ) \right],
  \label{eq:transformation}
  \end{equation}
  with $\hat{\mathbf{e}}_d$ being the unitary vector along axis $d$.

\subsubsection{Optimization}
\label{sec:gradient_descent}
To find the minimum of the energy functional \eqref{eq:energy},
  we propose a gradient-descent approach with respect to the underlying
  deformation field through the following \gls*{pde}:
  \begin{equation}
  \frac{\partial u(\vec{x},t)}{\partial t} \propto - \frac{\partial E(\vec{u})}{\partial \vec{u}_k},
  \label{eq:general_gradient_descent}
  \end{equation}
  with $t$ being an artificial time parameter of the contour
  evolution, and $\vec{u}_k$ the parameters supporting the estimate
  $\hat{U}$ of the transformation at the current time point.
Now, we introduce \eqref{eq:energy} in \eqref{eq:general_gradient_descent}:
  \begin{align}
  \frac{\partial E(\vec{u})}{\partial \vec{u}_k} &=
  \frac{ \partial }{\partial \vec{u}_k} \Big\{
  C + \underset{l}{\sum}
  \underset{\vec{x} \in \Omega_l}{\sum} \mdist{f'}{l} \notag\\
  &+ \underset{\vec{x} \in \Omega}{\sum} \boldsymbol{\alpha} \cdot u(\vec{x})^{\circ2}
  + \underset{\vec{x} \in \Omega}{\sum} \boldsymbol{\beta} \cdot (\nabla \cdot u(\vec{x}))^{\circ2}
  \Big\}.
  \label{eq:gradient_descent}
  \end{align}

>>>>

First, we assume independence between pixels, and thus break down the
  global data likelihood into a product of pixel-wise conditional probabilities:
  \begin{equation}
  P(F \mid U,\Omega) = \underset{l}{\prod} \underset{\vec{r}\in \Omega_l}{\prod}
    P\left( \vec{f}' \mid U \right),
  \label{eq:bayes_aposteriori}
  \end{equation}
  where $\vec{f}' = F(\vec{r}')$ is the feature vector at the displaced
  position $\vec{r}'$ (\autoref{eq:transform}) of the multispectral target
  volume.
For convenience, and because it has been shown to be appropriate approximations
  \citep{cuadra_comparison_2005}, we introduce two assumptions for each
  region $\Omega_l$:
  1) the features are i.i.d.; and 2) they can be modeled by multivariate normal
  distributions:
  \begin{equation}
  P\left( \vec{f}' \mid U,\Omega_l \right) = \mathcal{N} \left( \vec{f}' \mid \Theta_l \right),
  \label{eq:likelihood}
  \end{equation}
 	where $\Theta_l = \lbrace \boldsymbol{\mu}_l, \boldsymbol{\Sigma}_{l} \rbrace$ are the
 	descriptors of region $\Omega_l$.
We then insert \autoref{eq:likelihood} into \autoref{eq:bayes_rule} to obtain the full
  formulation of the \emph{data term} of our registration model:
 	\begin{align}
  P( F \mid U, \Omega ) &= \underset{l}{\prod} \underset{\vec{r} \in \Omega_l}{\prod}
  \mathcal{N} ( \vec{f} \mid \boldsymbol{\mu}_l, \boldsymbol{\Sigma}_{l} ) \notag\\
  &= \underset{l}{\prod} \underset{\vec{r} \in \Omega_l}{\prod} \frac{1}{ \sqrt{(2\pi)^{C}\,\left|\boldsymbol{\Sigma}_{l}\right|}}\,{e^{\left(-\frac{1}{2}
  \mdist{f'}{l} \right)}},
  \label{eq:pdf}
  \end{align}
  using $\mdist{f}{l}$ to denote the squared \emph{Mahalanobis distance} of $\vec{f}$ with respect
  to the descriptors of region $l$ as
  $\mdist{f}{l} = (\vec{f} - \boldsymbol{\mu}_l)^T \, {\boldsymbol{\Sigma}_l}^{-1} \, (\vec{f} - \boldsymbol{\mu}_l)$.

We choose a Thikonov regularization prior as follows:
  \begin{equation*}
  P(U) = \underset{\vec{r}}{\prod} p(u(\vec{r})) =
  \underset{\vec{r}}{\prod} p_0(u(\vec{r})) \, p_1(u(\vec{r})),
  \end{equation*}
  with further:
  \begin{align*}
  p_0(u(\vec{r})) &= \mathcal{N}( u(\vec{r}) \mid 0, A^{-1}), \notag\\
  p_1(u(\vec{r})) &= \mathcal{N}(  \nabla \cdot u(\vec{r}) \mid 0, B^{-1}),
  \end{align*}
  imposing that the distortion and its gradient have zero
  mean and variance governed by $A$ and $B$.
Since the anisotropy is generally aligned with the imaging axes, these will be simplified
  in the following for the sake of clarity:
  \begin{align}
    p_0(u(\vec{r})) &= \underset{\vec{r}}{\sum} \mathcal{N}( u(\vec{r}) \mid 0,
      (\boldsymbol{\alpha}^{\circ\frac12}\,\vec{I}_n)^{-1}), \notag\\
    p_1(u(\vec{r})) &= \underset{\vec{r}}{\sum} \mathcal{N}( \nabla \cdot u(\vec{r}) \mid 0,
      (\boldsymbol{\beta}^{\circ\frac12}\,\vec{I}_n)^{-1}).
  \label{eq:priors}
  \end{align}

Finally, the \gls{map} problem is adapted into a variational one applying the
  following log-transform:
  \begin{align}
  E(F \mid U) &= -\log \underset{l}{\prod}
  \underset{\vec{r} \in \Omega_l}{\prod}
  \mathcal{N} \left( \vec{f}' \mid \Theta_l \right)\,p_0( u(\vec{r}))\,p_1( u(\vec{r})) \notag\\
  &= C + \underset{l}{\sum}
  \underset{\vec{r} \in \Omega_l}{\sum}
  \mdist{f'}{l} \notag\\
  &+ \underset{\vec{r} \in \Omega}{\sum} \boldsymbol{\alpha} \cdot u(\vec{r})^{\circ2}
  + \underset{\vec{r} \in \Omega}{\sum} \boldsymbol{\beta} \cdot (\nabla \cdot u(\vec{r}))^{\circ2},
  \label{eq:energy}
  \end{align}
  that is the dual expression to the energy functional corresponding
  to a discrete \gls*{acwe} framework \citep{chan_active_2001}
  with anisotropic regularization as studied in
  \citep{nagel_investigation_1986}.
We provide a proof of duality in {\color{red} [REF figshare?]}.

@@

\subsubsection{Deformation model}
\label{sec:deformation_model}
Let us denote $\{\vec{c}_i\}_{i=1 \ldots N_c}$ the nodes of one or several prior
  surface(s).
In our application, these surfaces are extracted using \emph{FreeSurfer}
  \citep{fischl_freesurfer_2012} in the case of real datasets.
The transformation from the structural space into the coordinate space of the
  target image is achieved through a dense deformation field $u(\vec{r})$, such that:
  \begin{equation}
  \vec{c}_i' = U\{\vec{c}_i\} = \vec{c}_i + u(\vec{c}_i),
  \label{eq:nodes_tfm}
  \end{equation}
  where $U$ is defined in \eqref{eq:transform}.
Since the nodes of the anatomical surfaces likely lay off-grid, it is required to
  derive $u(\vec{r})$ from a discrete set of parameters $\{\vec{u}_k\}_{k=1 \ldots K}$.
Densification is achieved through a set of associated basis functions $\psi_k$:
  \begin{equation}
  u(\vec{r}) = \sum_k \psi_k(\vec{r}) \vec{u}_k.
  \label{eq:intp_kernel}
  \end{equation}
%
In our implementation, $\psi_k$ is chosen to be a tensor-product B-Spline kernel
  of degree 3 ($B_3$).
Then, introducing \eqref{eq:intp_kernel} into \eqref{eq:nodes_tfm} and replacing
  $\psi$ by the actual kernel function, the transformation writes:
  \begin{equation}
    \vec{c}_i' = \vec{c}_i + \sum_k \left[ \vec{u}_k \, \underset{d}{\prod}
      B_3( (\vec{c}_i - \vec{r}_k) \cdot \hat{\mathbf{e}}_d ) \right],
  \label{eq:transformation}
  \end{equation}
  with $\hat{\mathbf{e}}_d$ being the unitary vector along axis $d$.

\subsubsection{Optimization}
\label{sec:gradient_descent}
To find the minimum of the energy functional \eqref{eq:energy},
  we propose a gradient-descent approach with respect to the underlying
  deformation field through the following \gls*{pde}:
  \begin{equation}
  \frac{\partial u(\vec{r},t)}{\partial t} \propto - \frac{\partial E(\vec{u})}{\partial \vec{u}_k},
  \label{eq:general_gradient_descent}
  \end{equation}
  with $t$ being an artificial time parameter of the contour
  evolution, and $\vec{u}_k$ the parameters supporting the estimate
  $\hat{U}$ of the transformation at the current time point.
Now, we introduce \eqref{eq:energy} in \eqref{eq:general_gradient_descent}:
  \begin{align}
  \frac{\partial E(\vec{u})}{\partial \vec{u}_k} &=
  \frac{ \partial }{\partial \vec{u}_k} \Big\{
  C + \underset{l}{\sum}
  \underset{\vec{r} \in \Omega_l}{\sum} \mdist{f'}{l} \notag\\
  &+ \underset{\vec{r} \in \Omega}{\sum} \boldsymbol{\alpha} \cdot u(\vec{r})^{\circ2}
  + \underset{\vec{r} \in \Omega}{\sum} \boldsymbol{\beta} \cdot (\nabla \cdot u(\vec{r}))^{\circ2}
  \Big\}.
  \label{eq:gradient_descent}
  \end{align}

### 2014-10-21 Publications/2013-TMI/06-results.tex
updated all

\section{Results and discussion}
\label{sec:results}

Please! Write me ASAP.

>>>>

% -*- root: 00-main.tex -*-
\section{Results and discussion}
\label{sec:results}

\subsection{Proof of concept}
\label{sec:results_phantom}

\subsection{Susceptibility distortion correction}
\label{sec:results_phantom}

\subsection{Discussion}
\label{sec:discussion}
Don't forget to mention other potential applications.

We implemented the methodology upon the widely used
Insight Registration and Segmentation
Toolkit~\footnote{\url{http://www.itk.org}} (ITK)
for its computational benefits, the standardized code, and
with the aim at making the procedure publicly available
when ready for sharing with the research community.
